---
title: 'Lab #1'
author: "Lab Group 11"
date: "January 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```

## Link to our group's repo: https://github.com/dapengh/stat585-lab1_group11.git

## Deliverable 1
class. 

## Deliverable 2
Several packages needed to be installed (it's strange there isn't a check in the code that sees if you have the needed libraries, and installs them if not). That was easy to fix. But Gina (other people should chime in) got an error Rcpp.Rmd file. 

I had an issue in installing a package called "emo". When I was trying to use <tt>`install.package()`<tt>, it says "package ‘emo’ is not available". So I searched it on google and found that "emo" package is not available on cran. I need to install it from github using package <tt>`devtools`<tt>.

```{r}
weather_sample <- read_fwf("ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn-v2.5-stations.txt",col_positions = fwf_widths(c(2,1,2,6,8,9,5,2,30,6,6,6,2),col_names = c("COUNTRY CODE ", "NETWORK CODE","ID PLACEHOLDERS (\"00\")","COOP ID", "LATITUDE", "LONGITUDE", "ELEVATION","STATE", "NAME", "COMPONENT 1 (COOP ID)","COMPONENT 2 (COOP ID)","COMPONENT 3 (COOP ID)", "UTC OFFSET")))


```